---
title: "Gill_Sarah_ML_PS2"
author: "Sarah Gill"
date: "1/27/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Documents/GitHub/problem-set-2")

```

```{r}
library(readr)
library(rcfss)
set.seed(1234)
```


1. Estimate the MSE of the model using the traditional approach. That is, fit the linear
regression model using the entire dataset and calculate the mean squared error for the entire dataset.
```{r}

nes2008_df <- read_csv("nes2008.csv")

regn_model <- glm(biden~female+age+educ+dem+rep, data = nes2008_df)

summary(regn_model)

(mse <- augment(regn_model, newdata = nes2008_df) %>%
  mse(truth = biden, estimate = .fitted))

```
Present and discuss your results at a simple, high level.

mse = 395.27

That seems large.



2. Calculate the test MSE of the model using the simple holdout validation approach.
```{r simple_holdout}

nes_split <- initial_split(data = nes2008_df, 
                            prop = 0.5) #split the data in half
nes_train <- training(nes_split) #random subsample to train
nes_test <- testing(nes_split)

nes_lm <- glm(biden~female+age+educ+dem+rep, data = nes_train) #fit model on training data

(train_mse <- augment(nes_lm, newdata = nes_train) %>%
  mse(truth = biden, estimate = .fitted))

(test_mse <- augment(nes_lm, newdata = nes_test) %>%
  mse(truth = biden, estimate = .fitted))

```

This seems wrong!.....


3.
```{r}

```



